
\section{Work Experience}
{Work Experience}

\href{https://www.deshaw.com/}
{\textbf{D. E. Shaw \& Co., L.P.}}
\par
Quantitative Developer Intern -- Quantititive Options Team
\hfill
\textbf{\DatestampYM{2018}{05}} --
\textbf{\DatestampYM{2018}{08}}

\SmallEntryGap
\begin{detail}
Studied options market micro-structures and their predictive power over market makers' delta hedging strategies.
Used the research results to design a low-latency model for predicting trade directions,
and implemented a prototype model able to perform real-time trading.
\end{detail}
\EntryGap
\href{https://www.quora.com/}
{\textbf{Quora Inc.}}
\par
Software Engineering Intern -- Platform Team
\hfill
\textbf{\DatestampYM{2017}{05}} --
\textbf{\DatestampYM{2017}{08}}

\SmallEntryGap
\begin{detail}
Implemented a error transpiler on top of the Javascript error reporting pipeline to decode and delegate unintelligible stack traces at web scale.
Additionally, designed and implemented a developer tool that enabled developers to adopt another user's settings and variables for debugging.
\end{detail}

\EntryGap
\href{https://www.kensho.com/}
{\textbf{Kensho Technologies Inc.}}
\par
Software Engineering Intern
\hfill
\textbf{\DatestampYM{2016}{05}} --
\textbf{\DatestampYM{2016}{08}}

\SmallEntryGap
\begin{detail}
Designed the abstraction and implementation of unit-aware timeseries with S-expression support into the product backbone. Created a new lab feature using automated feature selection, linear transformation and KNN to predict currency exchange rates and implemented it in collaboration with the research team.
\end{detail}
