
\section{Independent Project Experience}
{Independent Project Experience}
\href{https://github.com/notmahi/learned-k-server}
{\textbf{Learning-Augmented $k$-server Algorithms}}
\par
Learning-Augmented Algorithms class project, Prof. Piotr Indyk
\hfill
\textbf{\DatestampYM{2019}{02} --
\DatestampYM{2019}{05}}
\SmallEntryGap
\begin{detail}
$\bullet$ Designed both supervised and unsupervised learning-augmented algorithms for the $k$-server problem when the requests are sampled from a well-behaved distribution.

$\bullet$ Showed that it is possible for us to learn a model that achieves a constant competitive ratio independent of $k$ when the requests are drawn from a Gaussian.

$\bullet$ Open-sourced the machine learning approach at \texttt{https://github.com/notmahi/learned-k-server}
\end{detail}
\EntryGap
\href{https://www.youtube.com/watch?v=vVIKaj2X-OE}
{\textbf{\textit{Manta}: A Maritime Rescue Device}}
\par
The Product Engineering Process project (patent pending)
\hfill
\textbf{\DatestampYM{2018}{09} --
\DatestampYM{2018}{12}}
\SmallEntryGap
\begin{detail}
$\bullet$ Designed a new maritime rescue device that decreases the time to contact sailors fallen overboard by launching a large loop of rope with personal floation assitance devices attached to them.

$\bullet$ Created multiple product prototypes, as well as a full model with CAD, over the length of the semester with feedback from design industry experts and professional sailors.

$\bullet$ Created a business model that would allow launch and profitable production of this model, and thus submitted a patent application for this product.
\end{detail}
\EntryGap
\href{https://github.com/16lawrencel/dynamic-graphs}
{\textbf{Benchmarking State-of-the-art Dynamic Graph Algorithms}}
\par
Advanced Data Structrues class project, Prof. Eric Demaine
\hfill
\textbf{\DatestampYM{2017}{09} --
\DatestampYM{2017}{12}}
\SmallEntryGap
\begin{detail}
$\bullet$ Implemented the state-of-the-art dynamic graph and dynamic tree algorithms and open sourced them at \texttt{https://github.com/16lawrencel/dynamic-graphs}

$\bullet$ Showed that a link-cut tree based dynamic tree algorithm is much faster in practice than asymptotically equivalent Euler-tour tree based implementation.

$\bullet$ Crafted a large test set including a million nodes and up to 30 million operations for testing and benchmarking, and using that, found a bug in the previous standard implementation of the $O(\lg ^2 n)$ dynamic graph algorithm.
\end{detail}
\EntryGap
\href{https://alam-shahul.github.io/Polygami/}
{\textbf{Polygami -- Crease pattern generation for arbitrary voxel patterns}}
\par
Geometric Folding Algorithm class project, Prof. Eric Demaine
\hfill
\textbf{\DatestampYM{2017}{02} --
\DatestampYM{2017}{05}}
\SmallEntryGap
\begin{detail}
$\bullet$ Created a webapp for voxel pattern to crease pattern generation using previously proven theoretical results; available at \texttt{https://alam-shahul.github.io/Polygami/}

$\bullet$ Implemented the folding algorithms and designed new heuristics that speed up the crease pattern generation process.

$\bullet$ Showed that finding the minimum amount of paper for such a crease pattern is NP-complete.
\end{detail}

\EntryGap

\href{https://devpost.com/software/hackmit2018}
{\textbf{MoodBox -- Smart DJ using facial recognition}}
\par
Placed in Top 10 -- HackMIT 2018
\hfill
\textbf{\DatestampYM{2018}{09}}
\SmallEntryGap
\begin{detail}
$\bullet$ Used computer vision to track attendants at an event, and used that information to curate a Spotify playlist in real time from their public playlists.

$\bullet$ Managed the project and work division, and personally worked on the real-time spotify updates and track database management.
\end{detail}

\EntryGap
{\textbf {Bangladesh Mathematical Olympiad Online Forum}}
\par{Administrator and Moderator}
\hfill \textbf{\DatestampYM{2012}{01} -- Present}
\SmallEntryGap
\begin{detail}
$\bullet$ Administrated and moderated the most active platform on math and science in Bangladesh. 

$\bullet$ Integrated $\LaTeX$, integrated anti-spam measurements, and modeled the forum according to user feedback.
\end{detail}
